Labeled object representation and manipulation with ITK

### 2007-06-12 article/Article.tex
more of the article
darcs-hash:20070612082030-2fc9d-96f7cbe63e59ef1fa99184f9679c338d39d72a85.gz

Because the objects are often get from a labeled image oor from a binary image,
those filters have been made for binary, and labeled images.

@@

\subsubsection{LabelObject}

\subsubsection{ShapeLabelObject}

\subsubsection{StatisticsLabelObject}

\subsubsection{AttributeLabelObject}

@@

To use that feature, a developer only have to subclass {\em InPlaceLabelCollectionImageFilter} and
implement the {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )}, to get easy thread
support (see the previous section), or the {\em virtual void GenerateData()} if the filter is not threadable. In that last case,
the only image to manipulate is the one get with the {\em GetOutput()} method, which is the input image if the filter runs in place, or a copy of the input image if the filter is not running in place.

@@

ITK is currntly lacking a good way to manipulate the binary objects. That contribution I hope to have mostly
filled that lack.

>>>>

Because the objects are often get from a labeled image or from a binary image,
those filters have been made for binary, and labeled images.

@@

% \subsubsection{LabelObject}
% 
% TODO
% 
% \subsubsection{ShapeLabelObject}
% 
% TODO
% 
% \subsubsection{StatisticsLabelObject}
% 
% TODO
% 
\subsubsection{AttributeLabelObject}

@@

To use that feature, a developer only have to subclass {\em InPlaceLabelCollectionImageFilter} and
implement the {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )}, to get easy thread
support \footnote{see the previous section}, or the {\em virtual void GenerateData()} if the filter is not threadable. In that last case,
the only image to manipulate is the one get with the {\em GetOutput()} method, which is the input image if the filter runs in place, or a copy of the input image if the filter is not running in place.

@@

ITK is currently lacking a good way to manipulate the binary objects. That contribution I hope to have mostly
filled that lack.
